Annotations on Quantum Pseudorandomness and $k$-Designs

### 2021-11-12 Complexity/LMNTheorem/paper.tex
Beginnings of UGC project

\subsection{Characters}
We introduce some stepping stones defining the tools used in the Fourier Analysis of boolean functions. Many of these tools can be defined using techniques from Representation Theory of Finite Groups, but for the sake of briefity, we will not delve into those concepts here in detail. Instead, we will provide remarks and snippets on relevant topics along with references to some literature at the end of the section. Our presentation follows that of \cite{hatami}. \newline

Let us first define some general concepts for any finite abelian group $G$. A group homomorphism from $\chi: G \rightarrow \mathbb{C}^*$ is called a \emph{character} of $G$ where $\mathbb{C}^* = \mathbb{C}/\{0\}$ is the multiplicative group of the complex numbers. We call the homomorphism $\chi_0:G \rightarrow \mathbb{C}^*, \; \chi_0 = 1$ the \emph{trivial character} of $G$. By definition, for $a,b \in G$,
\begin{equation} \label{homo}
\chi(a + b) = \chi(a)\chi(b)
\end{equation}
for all characters $\chi$. \newline

@@

\begin{remark}{\emph{(Generalizations of Fourier Analysis)}}
The above properties on characters can be shown through techniques in Representation Theory. For instance, we know representations of finite groups are group homomorphisms into the group of linear automorphisms of a suitable finite-dimensional complex vector space $\rho: G \rightarrow GL(V)$ where $GL(V)$ denotes the group of invertible linear operators on finite-dimensional complex vector space $V$. The \emph{characters} of $\rho$ are defined as $\chi_\rho(x) = Tr(\rho(x))$ where $Tr$ is the trace operator. It turns out that the representations of finite abelian groups are one-dimensional i.e isomorphic to $\mathbb{C}$. Thus, $\rho(x)$ will just be multiplying $\mathbb{C}$ by some scalar $\lambda_x \in \mathbb{C}^*$. In this case, we can show that indeed for any $a,b \in G$ and $\chi$ any character of $G$:
$$ \chi(a+b) = Tr(\rho(a+b)) = Tr(\rho(a)\circ\rho(b)) = \lambda_a \lambda_b = Tr(\rho(a))Tr(\rho(b)) = \chi(a)\chi(b)$$ Note that this relation does not hold for arbitrary finite groups since the trace is generally not multiplicative. In addition, for arbitrary finite group $G$, there is an inner product defined on the vector space spanned by the characters of \emph{irreducible} representations i.e representations containing no subspace invariant under the action of $G$. This inner product is defined as:

\[ \langle \chi_{\rho}, \chi_{\sigma} \rangle =
\frac{1}{|G|}\sum_{g \in G} \chi_{\rho}(g)\overline{\chi_{\sigma}(g)}\]

for irredudible representations $\rho: G \rightarrow GL(V_\rho)$ and $\sigma: G \rightarrow GL(V_\sigma)$. By an orthogonality argument similar to Theorem \ref{orthonormal}, we have that for irreducible representations $\rho, \sigma$, $ \langle \chi_{\rho}, \chi_{\sigma} \rangle = 1$ iff $\rho, \sigma$ denote the same representation else $\langle \chi_{\rho}, \chi_{\sigma} \rangle = 0$. For finite abelian group $G$, the one-dimensional representations above are irreducible.  Thus, for non-trivial character $\chi$,
%
 \[ |G|\langle \chi, \chi_0 \rangle = \sum_{g \in G} \chi(g)\chi_0(g) = \sum_{g \in G} \chi(g)  = 0 \]
%
where $\chi_0$ is the trivial character of $G$. This gives another proof of Lemma \ref{totalsum}. For more information on the Representation Theory of Finite Groups, see \cite{serre}, \cite{webb}.
\end{remark}

@@

\begin{definition}
  A function $f:\{0,1\}^m \times \{0,1\}^n \rightarrow \{0,1\}$ is called a \emph{pseudorandom function generator} if there exists no polynomial-time oracle Turing machine which can distinguish between the outputs from a true random oracle versus $f(s,_)$ for some random seed $s \in \{0,1\}^m$.
\end{definition}

>>>>

We introduce some stepping stones defining the tools used in the Fourier Analysis of boolean functions. Many of these tools can be defined using techniques from Representation Theory of Finite Groups, but for the sake of briefity, we will not delve into those concepts here in detail. Instead, we will provide remarks and snippets on relevant topics along with references to some literature at the end of the section. Our presentation follows that of \cite{hatami}. \newline

\subsection{Characters}
Let us first define some general concepts for any finite abelian group $G$. A group homomorphism from $\chi: G \rightarrow \mathbb{C}^*$ is called a \emph{character} of $G$ where $\mathbb{C}^* = \mathbb{C}/\{0\}$ is the multiplicative group of the complex numbers. We call the homomorphism $\chi_0:G \rightarrow \mathbb{C}^*, \; \chi_0 = 1$ the \emph{trivial character} of $G$. By definition, for $a,b \in G$,
\begin{equation} \label{homo}
\chi(a + b) = \chi(a)\chi(b)
\end{equation}
for all characters $\chi$. \newline

@@

\begin{remark}{\emph{(Generalizations of Fourier Analysis)}}
The above properties on characters can be shown through techniques in Representation Theory. For instance, we know representations of finite groups are group homomorphisms into the group of linear automorphisms of a suitable finite-dimensional complex vector space $\rho: G \rightarrow GL(V)$ where $GL(V)$ denotes the group of invertible linear operators on finite-dimensional complex vector space $V$. The \emph{characters} of $\rho$ are defined as $\chi_\rho(x) = Tr(\rho(x))$ where $Tr$ is the trace operator. It turns out that the representations of finite abelian groups are one-dimensional i.e isomorphic to $\mathbb{C}$. Thus, $\rho(x)$ will just be multiplying $\mathbb{C}$ by some scalar $\lambda_x \in \mathbb{C}^*$. In this case, we can show that indeed for any $a,b \in G$ and $\chi$ any character of $G$:
$$ \chi(a+b) = Tr(\rho(a+b)) = Tr(\rho(a)\circ\rho(b)) = \lambda_a \lambda_b = Tr(\rho(a))Tr(\rho(b)) = \chi(a)\chi(b)$$ Note that this relation does not hold for arbitrary finite groups since the trace is generally not multiplicative. In addition, for arbitrary finite group $G$, there is an inner product defined on the vector space spanned by the characters of \emph{irreducible} representations i.e representations containing no subspace invariant under the action of $G$. This inner product is defined as:
%
\[ \langle \chi_{\rho}, \chi_{\sigma} \rangle =
\frac{1}{|G|}\sum_{g \in G} \chi_{\rho}(g)\overline{\chi_{\sigma}(g)}\]
%
for irredudible representations $\rho: G \rightarrow GL(V_\rho)$ and $\sigma: G \rightarrow GL(V_\sigma)$. By an orthogonality argument similar to Theorem \ref{orthonormal}, we have that for irreducible representations $\rho, \sigma$, $ \langle \chi_{\rho}, \chi_{\sigma} \rangle = 1$ iff $\rho, \sigma$ denote the same representation else $\langle \chi_{\rho}, \chi_{\sigma} \rangle = 0$. For finite abelian group $G$, the one-dimensional representations above are irreducible.  Thus, for non-trivial character $\chi$,
%
 \[ |G|\langle \chi, \chi_0 \rangle = \sum_{g \in G} \chi(g)\chi_0(g) = \sum_{g \in G} \chi(g)  = 0 \]
%
where $\chi_0$ is the trivial character of $G$. This gives another proof of Lemma \ref{totalsum}. For more information on the Representation Theory of Finite Groups, see \cite{serre}, \cite{webb}.
\end{remark}

@@

\begin{definition}
  A function $f:\{0,1\}^m \times \{0,1\}^n \rightarrow \{0,1\}$ is called a \emph{pseudorandom function generator} if there exists no polynomial-time oracle Turing machine which can distinguish between the outputs from a true random oracle versus $f(s,-)$ for some random seed $s \in \{0,1\}^m$.
\end{definition}

### 2021-11-12 QIT/2Designs/final.tex
Beginnings of UGC project

  $$||T||_{\diamond} = \sup_d ||T \otimes I_d ||_{\infty} $$

@@

\subsubsection{Preliminaries on Markov Chains}
Let us introduce some definitions for properties of the Markov chains we are interested in. Although we assume familiarity with the definition of a Markov chain along with the its associated transition matrix $P$, we refer the reader to the reference \cite{cover} for greater detail. Recall that if $q^{(0)}$ is some initial  distribution over the $\Omega$ then $q^{(t)} = q^{(0)}P^t$. The \emph{stationary distribution} of a Markov chain $\pi$ is a probability distribution over $\Omega$ such that $\pi P = \pi$.
%
\begin{definition}
  A Markov chain is said to be \emph{irreducible} if there exists a path $s \rightsquigarrow j$ for every pair of states $s,j \in \Omega$.
\end{definition}
%
\begin{definition}
  A Markov chain is said to be \emph{periodic} at state $i \in \Omega$ if there exists a positive integer $T > 1$ such for that some initial distribution $q^(0)$, if $q_i^{(t)} > 0$ then $t \in \{a + Tm \mid m \in \mathbb{N}\}$. A Markov chain is deemed as \emph{aperiodic} if none of its states are periodic.
\end{definition}
\noindent Hence, a Markov chain containing self-loops i.e transitions to itself with positive probability, is aperiodic.
%
\begin{definition}
  A Markov chain is \emph{ergodic} if it is aperiodic and irreducible.
\end{definition}
\noindent As the below theorem reveals, ergodicity shows that any initial distribution over $\Omega$ converges to a unique stationary distribution.
%
\begin{theorem}
  If a Markov chain is ergodic, then it converges to a unique stationary distributon $\pi$ i.e $P$ has a unique eigenvector with eigenvalue one.
\end{theorem}
%
\noindent One can view this as special case of the \emph{Perron-Frobenius Theorem for Regular Matrices}.
%
\begin{theorem} \label{perron}
  Suppose that $P$ is transition matrix with positive entries and also that $P_{ij}^{k} > 0$ for some sufficiently large $k$ and for all entries $i,j$ (Regularity). Then the following must hold:
  \begin{enumerate}
    \item The largest eigenvalue must be real and postive
    \item The largest left eigenvector $\pi$ must be positive and unique
    \item $\lim_{k \rightarrow \infty} qP^{(k)} = \pi$ for all initial distributions $q$.
  \end{enumerate}
\end{theorem}
\noindent Since our matrices are stochastic i.e $\sum_{j} P_{ij} = 1$ for all $i$, our largest eigenvalue will be one. Furthermore, the left eigenvector of eigenvalue one will be the stationary distribution $\pi$. Since our Markov chain is both irreducible and aperiodic, it must be regular as well.
%
\begin{remark}
  It is not difficult to find counterexamples to Theorem \ref{perron} if the Markov chain is not ergodic. For instance, consider the chain

@@

%\subsection{Tying Some Loose Ends}

%Finally, we state the proof of Theorem \ref{maintheorem}. \newline
%\begin{proof}[(Proof of Theorem \ref{maintheorem})]
%\end{proof}

\bibliographystyle{amsplain}
\bibliography{biblio}

>>>>

  $$||T||_{\diamond} = \sup_d ||T \otimes I_d ||_{\infty} = \sup_d \sup_{X \neq 0} \frac{||(T \otimes I_d)(X)||_1}{||X||_1}$$

@@

\subsubsection{Preliminaries on Markov Chains}
Let us introduce some definitions for properties of the Markov chains we are interested in. Although we assume familiarity with the definition of a Markov chain along with its associated transition matrix $P$, we refer the reader to the reference \cite{cover} for greater detail. Recall that if $q^{(0)}$ is some initial distribution over a finite set of states $\Omega$ then $q^{(t)} = q^{(0)}P^t$ describes the distribution over $\Omega$ after $t \geq 1$ steps. The \emph{stationary distribution} of a Markov chain $\pi$ is a distribution over $\Omega$ such that $\pi P = \pi$.
%
\begin{definition}
  A Markov chain is said to be \emph{irreducible} if there exists a path $s \rightsquigarrow j$ for every pair of states $s,j \in \Omega$.
\end{definition}
%
\begin{definition}
  A Markov chain is said to be \emph{periodic} at state $i \in \Omega$ if there exists a positive integer $T > 1$ such for that some initial distribution $q^(0)$, if $q_i^{(t)} > 0$ then $t \in \{a + Tm \mid m \in \mathbb{N}\}$. A Markov chain is deemed as \emph{aperiodic} if none of its states are periodic.
\end{definition}
\noindent Hence, a Markov chain containing self-loops i.e transitions to itself with positive probability, is aperiodic.
%
\begin{definition}
  A Markov chain is \emph{ergodic} if it is aperiodic and irreducible.
\end{definition}
\noindent As the below theorem reveals, ergodicity shows that any initial distribution over $\Omega$ converges to a unique stationary distribution.
%
\begin{theorem}
  If a Markov chain is ergodic, then it converges to a unique stationary distributon $\pi$ i.e $P$ has a unique eigenvector with eigenvalue one.
\end{theorem}
%
\noindent One can view this as special case of the \emph{Perron-Frobenius Theorem for Regular Matrices}.
%
\begin{theorem} \label{perron}
  Suppose that $P$ is transition matrix with positive entries and also that $P_{ij}^{k} > 0$ for some sufficiently large $k$ and for all entries $i,j$ (Regularity). Then the following must hold:
  \begin{enumerate}
    \item The largest eigenvalue must be real and postive
    \item The largest left eigenvector $\pi$ must be positive and unique
    \item $\lim_{k \rightarrow \infty} qP^{(k)} = \pi$ for all initial distributions $q$.
  \end{enumerate}
\end{theorem}
\noindent Since our matrices are stochastic i.e $\sum_{j} P_{ij} = 1$ for all $i$, our largest eigenvalue will be one. Furthermore, the left eigenvector of eigenvalue one will be the stationary distribution $\pi$. Since our Markov chain is both irreducible and aperiodic, it must be regular as well.
%
\begin{remark}
  It is not difficult to find counterexamples to Theorem \ref{perron} if the Markov chain is not ergodic. For instance, consider the chain

@@

\subsection{Tying Some Loose Ends}
We dedicate this section to addressing some details glossed over in the previous two sections. In particular, the vanishing rate of the non-diagonal terms must be handled before considering the proof for Theorem \ref{maintheorem}. First, the proof from Lemma \ref{mainlemma} to the more general statement of Corollary \ref{maincorollary} must be given. The proof will demonstrate how the more restricted set of initial states used in Lemma \ref{mainlemma} can easily generalize to all initial states, even those with negative diagonal coefficients.
%
\begin{proof}[(Proof of Corollary \ref{maincorollary})]
 Begin by first noting that Lemma \ref{mainlemma} immediately implies the corollary for coeffcients of non-diagonal terms $\gamma(p,q), \; p \neq q$. Thus, it suffices to only consider the diagonal terms $\gamma(p,p)$. Now from the observations made in Theorem \ref{haarevol} and linearity, we can view the expected coeffcients $\mathbb{E}_{W}\gamma_W(p,p)$ over all $t$-length random circuits $W$ to follow that of a random walk over the diagonal states. Let $g_t(p;q)$ be the probability of arriving at state $p,p$ in $t$-steps starting from state $q,q$ via the random walk defined in Theorem \ref{haarevol}. This means that $g_0(p,q) = \delta_{p,q}$. We can calculate the expected coeffcients as
 \begin{equation}
   \gamma_t(p,p) = \sum_{q \neq 0} g_t(p,q)\gamma_0(q,q)
 \end{equation}
\end{proof}
By performing an effective normalization, we can generalize Lemma \ref{mainlemma} to the corollary as follows: Consider first the inequality for the 2-norm
%
\begin{align*}
\sum_{p \neq 0} \left( \gamma_t(p,p) - \frac{\sum_{q \neq 0} \gamma_0(q,q)}{4^n -1}\right)^2
& = \sum_{p \neq 0} \left(\sum_{q\neq 0} \gamma_0(q,q) \left( g_t(p,q) - \frac{1}{4^n -1} \right)\right)^2 \\
& \leq \left( \sum_{q \neq 0} |\gamma_0(q,q)|^2 \right) \sum_{q' \neq 0} \sum_{p \neq 0 }\left( g_t(p,q') - \frac{1}{4^n -1} \right)^2 \\
& \leq  \left( \sum_{q \neq 0} |\gamma_0(q,q)|^2 \right) (4^n -1)\epsilon \\
& = 4^n\epsilon \cdot Tr(\rho^2) \\
& \leq 4^n \epsilon
\end{align*}

The first inequality arises from the Cauchy-Schwartz inequality and rearranging terms. The second inequality is Lemma \ref{mainlemma}, and the final inequality is just $Tr(\rho^2) \leq 1$ for any state $\rho$. Invoking Lemma \ref{mainlemma} shows that the above inequality holds for $t \geq n(n + \log4^n/\epsilon) = Cn((\log 4 + 1)n + \log1/\epsilon)$ for sufficiently large $C$ chosen in the Lemma. Now choose a larger constant $C'$ dominating the righthand expression to prove the desired result. The 1-norm case proceeds similarly:
%
\begin{align*}
 \sum_{p \neq 0} \left( \gamma_t(p,p) - \frac{\sum_{q \neq 0} \gamma_0(q,q)}{4^n -1}\right)
 & = \sum_{p \neq 0} \left|\sum_{q\neq 0} \gamma_0(q,q) \left( g_t(p,q) - \frac{1}{4^n -1} \right) \right| \\
 & \leq \sum_{q \neq 0}|\gamma_0(q,q)|\sum_{p \neq 0} \left| g_t(p,q) - \frac{1}{4^n -1} \right| \\
 & \leq \sum_{q \neq 0}|\gamma_0(q,q)| 2^n \epsilon \\
 & \leq 2^n \epsilon
\end{align*}
%
\subsubsection{First and Second Moments Convergence for 1-designs}
We show that our scheme acts an approximate 1-design in the sense below:
%
\begin{lemma} \label{onedesign}
  \begin{equation}
    \sum_{p \neq 0} (\mathbb{E}_{W_t}|\gamma_{W_t}(p)|)^2 \leq \epsilon
  \end{equation}
  after $t \geq n\log1/\epsilon$

and
\begin{equation}
  \sum_{p \neq 0} \mathbb{E}_{W_t}|\gamma_{W_t}(p)| \leq \epsilon
\end{equation}
after $t \geq n\log n/\epsilon$
\end{lemma}

Note that since we are considering 1-designs here, we index through only one $n$-string $p$. From subsection \ref{eigenanalysis}, recall that applying a unitary $U \sim \mathbb{U}(4)$ completely randomizes the qubit pair if at least one of them are non-zero i.e take basis operators $\sigma_1,\sigma_2,\sigma_3$ in the Pauli basis. This means that if sites $i,j$ are picked, then coefficients of basis states $\gamma(p)$ where $p_i \neq 0$ or $p_j \neq 0$ vanish under $U$. In this case, we say that sites $i,j$ have been \emph{hit}. For an unitary sampled over a universal distribution $U \sim \mu$, the coefficients shrink by a factor $1 - \Delta$ where $\Delta$ is deemed as a gap for distribution $\mu$. Hence, sites which have been hit $r$ times shrink by a factor $(1- \Delta)^r$. The case for Haar distribution follows the analysis of the standard coupon collectors problem (see \cite{raghavan} for an introduction). However, the case for any universal distribution follows from a similar line of thinking as demonstrated in the proof of Lemma \ref{onedesign}.

\begin{proof}[(Proof of Lemma \label{onedesign})]
  Let us first focus on the case for the coefficient of a specific basis state $\mathbb{E}_{W_t} |\gamma_{W_t}(p)|$. From the discussion above, the coefficient shrinks by a factor of $1 -\Delta$ if a pair with at least one non-zero site is picked. The probablity of this event occuring is easily calculated to be
  $$ 1 - \frac{(n-d)(n-d-1)}{n(n-1)} \geq 1 - \frac{n-d}{n} = \frac{d}{n} $$
  if $d$ denotes the number of non-zeros contained in $n$-string $p$. This gives us the recurrence inequality:
  \begin{equation*}
    \mathbb{E}_{W_t}|\gamma_{W_t}(p)| \leq ((1- \Delta)(d/n) + (1 - d/n))\cdot |\gamma_{W_{t-1}}(p)| = \left(2 - \frac{\Delta d}{n} \right)\cdot |\gamma_{W_{t-1}}(p)|
  \end{equation*}
Iterating this $t$ times gives the inequality:
\begin{align*}
  \mathbb{E}_{W_t}|\gamma_{W_t}(p)| \leq \left(2 - \frac{\Delta d}{n}\right)^t |\gamma_0(p)| = \left(2 - \frac{\Delta d}{n}\right)^{n \cdot \frac{t}{n}} |\gamma_0(p)| \leq e^{-\Delta d  t/ n} |\gamma_0(p)|
\end{align*}
Summing over all $p$ then yields the total inequality
\begin{equation*}
  \sum_{p \neq 0} \mathbb{E}_{W_t}|\gamma_{W_t}(p)| \leq \sum_{d = 1}^n e^{-\Delta d t/n} \sum_{d(p) = d} |\gamma_0(p)|
\end{equation*}
where $d(p)$ is the number of non-zeros in string $p$. With th-- obvious bound $|\gamma_0(p)| \leq 1$, we give the total bound:
$$ \sum_{d(p) = d} |\gamma_0(p)| \leq {n \choose d} 3^d $$
This is easily seen as the number of basis states with exactly $d$ non-zero states since each non-zero site would take values in $\{\sigma_1, \sigma_2, \sigma_3\}$. Substituting this bound into the inequality above:
\begin{align*}
   \sum_{d = 1}^n e^{-\Delta d t/n} \sum_{d(p) = d} |\gamma_0(p)| \leq {n \choose d} (3e^{-\Delta t/n} )^d \leq (1 + 3e^{-\Delta t/n})^n -1
\end{align*}
where the last inequality is an invocation of the Binomial theorem. Setting $t \geq \frac{n}{\Delta} \log\frac{3n}{\epsilon}$ yields
\begin{equation*}
  \sum_{p \neq 0} \mathbb{E}_{W_t}|\gamma_{W_t}(p)| \leq \left(1 + \frac{\epsilon}{n} \right)^n - 1 = \mathcal{O}(\epsilon)
\end{equation*}
The bound for the 2-norm is dervied in a similar fashion. See \cite{harrlow}, Lemma 4.1 for the corresponding 2-norm bound.
The proof for Lemma \ref{onedesign} can be repurposed to prove rapid vanishing of the non-diagonal terms $\sigma_{p_1} \otimes \sigma_{p_2}$ as presented in the lemma below:
     \sum_{p \neq q} \left( \mathbb{E}_{W_t} |\gamma_{W_t}(p,q)|\right)^2 \leq \epsilon
  for $t \geq n\log\frac{1}{\epsilon}$
  and
    \sum_{p \neq q}  \mathbb{E}_{W_t} |\gamma_{W_t}(p,q)| \leq \epsilon
  From the analysis for the second moments given in Section \ref{eigenanalysis}, the cofficients decay by a factor of $1- \Delta$ if $\sigma_{p_{i}} \otimes \sigma_{p_{j}}$ is different from the state $\sigma_{q_{i}} \otimes \sigma_{q_{j}}$. Thus, picking at least one differing site will trigger a shrinking of the coefficient $\gamma(p,q)$. This motivates the setting of the parameter $d$ in the previous proof to be the number of \emph{non-differing sites}. This results in the same inequality
  $$ \mathbb{E}_{W_t}|\gamma_{W_t}(p,q)| \leq \left(2 - \frac{\Delta d}{n} \right)\cdot |\gamma_{W_{t-1}}(p,q)|$$
  which yields the identical inequality:
  \begin{equation*}
    \sum_{\substack{p \neq q \\ pq \neq 00}} \mathbb{E}_{W_t}|\gamma_{W_t}(p,q)| \leq \sum_{d = 1}^n e^{-\Delta d t/n} \sum_{d(p,q) = d} |\gamma_0(p,q)|
  \end{equation*}
  where $d(p,q)$ here would count the number of non-differing sites instead. We bound $\sum_{d(p,q) = d} |\gamma_0(p,q)| \leq {n \choose d} 4^d12^{n-d}$ to arrive at
  \begin{align*}
    \sum_{\substack{p \neq q \\ pq \neq 00}} \mathbb{E}_{W_t}|\gamma_{W_t}(p,q)| \leq \sum_{d = 1}^n e^{-\Delta d t/n} {n \choose d} 4^d12^{n-d} =  4^n \sum_{d = 1}^n{n \choose d} 3^{n-d} = 4^n(1 + 3e^{-\Delta t/n})^n -1)
  \end{align*}
  Set $t \geq \frac{n}{\Delta}(n\log{4} + \log{1/\epsilon})$ to finish the proof.

\begin{proof}[(Proof of Theorem \ref{maintheorem})]
  We are now in the position to prove the main result in respect to the \emph{diamond norm}. The following string of inequalities hold:
  \begin{align}
    ||\mathcal{G}_W - \mathcal{G}_H ||_{\diamond}^2
    & = \sup_d|| \mathcal{G}_W \otimes I_d - \mathcal{G}_W \otimes I_d||_{\infty} = \sup_{\rho} ||(\mathcal{G}_W \otimes I_n)(\rho) - (\mathcal{G}_H \otimes I_n)(\rho) ||_1^2 \\
    & \leq (2^{2(2n)})\sup_{\rho} ||(\mathcal{G}_W \otimes I_n)(\rho) - (\mathcal{G}_H \otimes I_n)(\rho) ||_2^2\\
    & = 2^{4n} \sup_{\rho} ||\sum_{p_1,p_2,p_3,p_4}\gamma_{\rho}(p_1,p_2,p_3,p_4) ( \mathcal{G}_W(\sigma_{p_1} \otimes \sigma_{p_2}) \otimes \sigma_{p_3} \otimes \sigma_{p_4} \\
    & - \mathcal{G}_H(\sigma_{p_1} \otimes \sigma_{p_2}) \otimes \sigma_{p_3} \otimes \sigma_{p_4} ) ||_2^2
  \end{align}
  The first inequality is just the standard inequality $||\rho||_1 \leq d ||\rho||_2$ where $d$ is the dimension of the system $\rho \in \mathbb{C}^{d}$. The last equality arises from linearity. Recall that
  $$ \mathcal{G}_{W_t}(\sigma_{p_1}\otimes \sigma_{p_2}) = \sum_{\substack{q_1,q_2 \\ q_1q_2 \neq 00}} g_t(p_1,p_2 ; q_1,q_2) \sigma_{q_1} \otimes \sigma_{q_2} $$
  over all random circuits of length $t$. Here $g_t$ represents the evolution of the coefficients as described by the combination of the analyses for the diagonal coefficients $g_t(p,p;q,q)$ and the non-diagonal ones presented above, culminating in Corollary \ref{maincorollary}. This yields
  \begin{align*}
     2^{4n} & \sup_{\rho} ||\gamma_{\rho}(p_1,p_2,p_3,p_4) \left( \mathcal{G}_W(\sigma_{p_1} \otimes \sigma_{p_2}) \otimes \sigma_{p_3} \otimes \sigma_{p_4} - \mathcal{G}_H(\sigma_{p_1} \otimes \sigma_{p_2}) \otimes \sigma_{p_3} \otimes \sigma_{p_4} \right) ||_2^2  \\
     & = 2^{4n} \sup_{\rho} || \sum_{p_3,p_4} \sum_{\substack{p_1,p_2,q_1,q_2 \\ q_1,q_2 \neq 00}}\gamma_{\rho}(p_1,p_2,p_3,p_4) \left( g_t(p_1,p_2;q_1,q_2) - \frac{\delta_{p_1,p_2}\delta_{q_1,q_2}}{2^n(2^n+1)} \right) \sigma_{q_1} \otimes \sigma_{q_2} \otimes \sigma_{p_3} \otimes \sigma_{p_4}   ||^2_2
  \end{align*}
  Taking the Hilbert-Schmidt norm and squaring the result kills the non-aligning terms to output
  \begin{align*}
  &   2^{4n} \sup_{\rho} \sum_{\substack{p_1,p_2,p_3,p_4,q_1,q_2 \\ q_1,q_2 \neq 0}} \gamma_{\rho}(p_1,p_2,p_3,p_4)^2 \left( g_t(p_1,p_2;q_1,q_2) - \frac{\delta_{p_1,p_2}\delta_{q_1,q_2}}{2^n(2^n+1)} \right)^2 \\
    & \leq 2^{4n} \sup_{\rho} \sum_{\substack{p_1,p_2,p_3,p_4,q_1,q_2 \\ q_1,q_2 \neq 0}} \gamma_{\rho}(p_1,p_2,p_3,p_4)^2 \epsilon^2 \\
    & \leq 2^{4n}\epsilon^2
  \end{align*}
  The last equality is from Lemma \ref{mainlemma}. This finally shows that
  \begin{equation}
    ||\mathcal{G}_W - \mathcal{G}_H ||_{\diamond} \leq 2^{2n}\epsilon
  \end{equation}
  when $t \geq Cn(n + \log{1/\epsilon})$. Take the final constant $C'$ to be sufficiently large such that $C'n(n + \log{1/\epsilon}) \geq Cn(n + \log{2^{2n}/\epsilon})$ to finish the proof.
\end{proof}
%Finally, we state the proof of Theorem \ref{maintheorem}. \newline
%\begin{proof}[(Proof of Theorem \ref{maintheorem})]
%\end{proof}

\newpage
\bibliographystyle{amsplain}
\bibliography{biblio}
